Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-05-01 paper/paper7/paper7.tex
sec 5

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 114 of constraints,\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} as described before. We evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these vocabularies, obtained from 33 SPARQL endpoints.

@@

%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
The number of evaluated triples and data sets differs between the vocabularies
as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
To be able to formulate hypotheses which apply for all vocabularies, 
we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class

@@

As the evaluation is based on three vocabularies, 
we cannot make valid general statements for all vocabularies,
but we can formulate several hypotheses to direct the further development of constraint languages.
As these hypotheses cannot be proved yet, 
they still have to be verified or falsified
by evaluating the quality of data represented by further well-established and newly developed vocabularies.
%More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
%For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
%(for \emph{QB} even three quarters).
%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
Almost 1/2 of all 213 constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
\begin{hyp}
%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
As a significant amount of 54\% of the constraints are either simple or complex constraints,
the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
\end{hyp}

Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
even though, 46\% of all constraints are \emph{vocabulary constraints},
indicates good data quality for all vocabularies with regard to their formal specifications.
\begin{hyp}
For all vocabularies, data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
\end{hyp}

%\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g. only 1.777 \emph{QB} violations} which indicates good data quality according to their formal specifications.
%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
which indicates bad data quality with regard to their formal specifications.

\begin{hyp}
Data represented by well-established vocabularies corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
Data represented by newly developed vocabularies, in contrast, does not correspond to their formal specifications.
\end{hyp}

@@

80\% of the \emph{QB} constraints are \emph{error constraints}.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
1/6 of the Disco violations are caused by \emph{error constraints} and
almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}
Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints.   
\end{hyp}

@@

\begin{hyp}
The further development of constraint languages should concentrate on how to express complex constraints as 44\% of all complex constraints are also serious ones.
\end{hyp}

>>>>

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 213 constraints of which we implemented for the data validation 114 constraints.\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} The reason is simply that more time is needed for the remaining implementation. We ensured, however, that the implementation is equally distributed over the classes and vocabularies we have. We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.

@@

%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
The numbers of evaluated triples and data sets differ between the vocabularies
as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
To be able to formulate hypotheses which apply for all vocabularies, 
we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class

@@

As the evaluation is based on three vocabularies, 
we cannot make valid general statements for all vocabularies,
but we can formulate several hypotheses to direct the further development of constraint languages.
As these hypotheses cannot be proved yet, 
they still have to be verified or falsified
by evaluating the quality of data represented by further well-established and newly developed vocabularies.
%More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
%For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
%(for \emph{QB} even three quarters).
%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
Almost 1/2 of all constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
\begin{hyp}
%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
As a significant amount of 54\% of the constraints are either simple or complex constraints,
the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
\end{hyp}

Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
even though, 46\% of all constraints are \emph{vocabulary constraints},
indicates good data quality for all vocabularies with regard to their formal specifications.

%\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
Moreover, while 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
This means that for the well-established vocabularies \emph{QB} and \emph{SKOS}, \emph{vocabulary constraints} are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.

For \emph{Disco}, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.

\begin{hyp}
Data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
\end{hyp}

@@

80\% of the \emph{QB} constraints are \emph{error constraints}.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
1/6 of the Disco violations are caused by \emph{error constraints} and
almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}
Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
\end{hyp}

@@

\begin{hyp}
There is significant demand for constraint languages that support the expression of complex constraints as 44\% of all complex constraints are also serious ones.
\end{hyp}
